%%
%% Template Experiments.tex
%%

% \chapter{Experiments}
% \label{cha:Experiments}

\section{Experiments}
\label{sec:experiments}

We test our algorithm on a Ubuntu 16.04 LTS server, with 4 2.4GHz
Intel Xeon processors and 128GB memory. The Maxflow v$3.04$
library developed by \citename{Kolmogorov:PAMI07} is used for
implementing the graph-cut algorithm. The cutting-plane algorithm
were performed using \citename{tsochantaridis2005large}'s
$\text{SVM}^{light}$ C++ library. We use Matlab R2016b's
quadratic programming engine for solving our learning algorithm's
objective problem. Regular SVM training and testing is
implemented by scikit-learn's svm module.


\subsection{Dataset preparation and configuration}
\label{sec:exp_data}

Our use CSI 300's daily market price (open, high, low, close,
volume), from 1st Jan 2015 to 31st Dec 2016, as our fundamental
dataset. There are $246 + 245 = 491$ samples in total. We then
calculated our technical analysis indicators (MACD-5, MACD-10,
KDJ-9) basing on this dataset. We further processed our dataset
with studentized residual normalization. Finally those samples
were split into two collections: 394 samples for training set and
97 samples for testing purpose. Our data are collected from Wind
dataset. During training stage, we used leave-one-out 10-fold
cross-validation to avoid over-fitting. The penalization
parameter $C$ in equation~\eqref{eq:ssvm_objective} was set to
$0.001$.

\subsection{Comparsion with SVM}
\label{sec:exp_compare}

\begin{table}
  \normalsize
  \centering
  \begin{tabular}{|l|c|c|}
    \hline
    {\sc Model} & {\sc Train Accuracy} & {\sc Test Accuracy}\\
    \hline \hline
    SSVM & 74.7\% & 63.1\% \\
    \hline
    SVM & 46.8\% & 22.6\% \\
    \hline
  \end{tabular}
  \caption{\label{tab:exp_compare} Results comparison
    between SSVM and SVM.}
\end{table}

From table~\ref{tab:exp_compare}, we can conclude that the train
accuracy and test accuracy of SSVM is better than that of SVM,
which proves that our model is better than the traditional
method.

\subsection{Real-world application}
\label{sec:exp_strategy}

According to the result of cluster analysis, the top 10 companies
which have the closest cooperation with other companies among the
CSI 300 are China Life Insurance Co., Sanan Optoelectronics,
Sinopec Group, Huadong Medicine Co., Shenzhen Inovance Technology
Co., Liaoning Cheng Da Co., Yongtai energy Limited by Share,
Wanxiang Qianchao Co., China Communications Construction Co., and
Bohai Financial Investment Holding Co.. All of these companies
are the industry leaders and they even have a great number of
hybrid businesses, especially the top 3 of them: Sinopec Group,
China Life Insurance Co. and Liaoning Cheng Da Co..

As the biggest chemical manufacturer in China and the No. 2
refiner in the world, the Sinopec Group has a series of
comparative advantages: its refining capacity accounts for half
of the China’s oil market share, and the distribution of its
refineries is close to the consumer market, resulting in its
strategic position. The complete pluralization and integration
and the balanced development of upriver and downstream lead to
its ability to fight fluctuation.

The controlling shareholder of China Life Insurance Co. is an
exclusive state-funded corporation. The strong background of
state-owned shareholder offers abundant of customer resource and
great financial investment platform. Recently, the China Life
Insurance Co. have reached strategic partnerships with many local
governments and famous enterprises. When the industry enters
differentiation phase, the position of industry leader shows up.
In 2016, Liaoning Cheng Da Co. properly handled the vaccine
safety problems, changed crises to opportunity and built out a
new distribution channel accessing to the county’s Centers for
Disease Control through the cooperation with domestic large-scale
circulation enterprises, maintaining the leading superiority in
the business. Along with the reform of state-owned enterprises,
the company successfully transformed into consolidation model.










%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End:
